\documentclass{exam}

\usepackage[overload]{exam-randomizechoices}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{tikz}
\usetikzlibrary{calc}

\begin{document}
\begin{questions}
        
    \question
    Which statement best describes a repeated game?

    \begin{checkboxes}
        \choice A repeated game is a strategic interaction where the same stage game is played multiple times, allowing players to condition their actions on past outcomes.
        \choice A repeated game is a one-shot game where players make simultaneous decisions without any knowledge of past interactions or future consequences.            
        \choice A repeated game is a game played over a single round but involves multiple players making sequential decisions.
        \choice A repeated game is a strategic interaction in which players’ payoffs depend only on their final actions, regardless of the game's duration or history.
    \end{checkboxes}

    \question
    Which statement best describes a strategy in a repeated game?

    \begin{checkboxes}
        \choice A strategy in a repeated game is a complete plan of action specifying a player's moves in each stage of the game, based on the history of previous actions by all players.
        \choice A strategy in a repeated game is the choice of a single action to be repeated in every stage, regardless of the opponent's behavior.            
        \choice A strategy in a repeated game is a plan that only determines a player's actions in the first stage of the game, leaving future stages unspecified.
        \choice A strategy in a repeated game is a set of random actions chosen independently at each stage without considering past interactions.
    \end{checkboxes}

    \question
    Consider the follow stage game:

    \[
        A = \begin{pmatrix}
            12 & -3\\
            -3 & 12
            \end{pmatrix}
            \qquad
        B = -A
    \]

    What are the utilities to both players when the game is repeated 3 times
    with the following strategies:

    \begin{itemize}
        \item For the row player: play row 1 first. If the column player played the
    first column, play row 1 for the next two turns if not: play row 1 followed
    by row 2.
        \item For the column player: play column 1 first then play the action that would
      be a best response to the last action picked by the row player.
    \end{itemize}

    \begin{checkboxes}
        \choice  Utility to row player: \(6\), utility to column player: \(-6\).
        \choice  Utility to row player: \(-6\), utility to column player: \(6\).
        \choice  Utility to row player: \(-12\), utility to column player: \(-12\).
        \choice  Utility to row player: \(0\), utility to column player: \(0\).
    \end{checkboxes}

\end{questions}
\end{document}
