\documentclass{exam}

\usepackage[overload]{exam-randomizechoices}
\usepackage{amsmath}
\usepackage{amsfonts}

\begin{document}
\begin{questions}
        
\question 
    Which statement best describes a Normal Form Game?
\begin{checkboxes}
   \choice 
A Normal Form Game is a representation of a strategic interaction where each
    player's actions and corresponding payoffs are displayed in a matrix, assuming simultaneous decision-making
   \choice 
A Normal Form Game is a representation of a game where players' actions are listed alongside their payoffs, but it assumes sequential decision-making at each stage of the game.
   \choice 
A Normal Form Game is a model that describes repeated interactions between players over multiple stages, focusing on the history of their actions.
    \choice
A Normal Form Game is a representation of a game where the payoffs depend solely
    on the order of moves rather than the players' chosen actions.
\end{checkboxes}



\question Which of the following games is zero-sum?
\begin{checkboxes}
   \choice 
        \begin{itemize}
            \item There are two players.
            \item Each player can choose 1 of three actions:
                $\mathcal{A}_1=\mathcal{A}_2=\{A, B, C\}$
            \item For any choices made by all the players they all get a payoff
                of 0.
        \end{itemize}
   \choice 
        Rock Paper Scissors but if both players choose Rock then they both win.
   \choice 
        \begin{itemize} 
            \item There is 1 player.
            \item \(\mathcal{A}_1=\{1, 2, ,\}\)
            \item \(u_1(1)=-u_1(2)=u_1(3)=-u_1(4)=1\) for all \(A \in \mathcal{A}_1\)
        \end{itemize}
\end{checkboxes}

\question Which of the matrix representations corresponds to the following game:

    \begin{quote}
        It has snowed on the road leading to two neighbours' houses. Each
        neighbour can either wait for the other to shovel the snow or shovel the
        snow. If they both wait then the road is not cleared. They would both
        prefer to not shovel.
    \end{quote}

\begin{checkboxes}
   \choice 
        \[
            A = \begin{pmatrix}
                5 & 4\\
                6 & 0
                \end{pmatrix}
                \qquad
            B = \begin{pmatrix}
                5 & 6\\
                4 & 0
                \end{pmatrix}
        \]
   \choice 
        \[
            A = \begin{pmatrix}
                5 & 6\\
                4 & 0
                \end{pmatrix}
                \qquad
            B = \begin{pmatrix}
                5 & 4\\
                6 & 0
                \end{pmatrix}
        \]
   \choice 
        \[
            A = \begin{pmatrix}
                5 & 6\\
                4 & 0
                \end{pmatrix}
                \qquad
            B = \begin{pmatrix}
                5 & 6\\
                4 & 0
                \end{pmatrix}
        \]

\end{checkboxes}
\end{questions}
\end{document}
