\documentclass[12pt,a4paper]{article}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{float}
\usepackage{tikz}
\usetikzlibrary{shapes, arrows, positioning}


\usepackage{amsmath,amssymb,mdframed}   % AMS package gives better equation layouts
\setcounter{page}{2}                    % sets first page number to 2
\setlength{\oddsidemargin}{-0.25in}     % set left margin
\setlength{\textwidth}{6.5in}           % set text width
\setlength{\topmargin}{-0.5in}          % controls layout at
\setlength{\headsep}{0.5in}             % top of page
\setlength{\textheight}{9.0in}          % set text length



\makeatletter
\renewcommand{\@oddhead}{\hfill MA3604/18}  % sets header % TODO fix header
\renewcommand{\@oddfoot}{\hfil \arabic{page} \hfil}    % sets page footer
\makeatother

\renewcommand{\labelenumi}{\arabic{enumi}} % Sets the first level of enumerate to be arabic (normal) numbers
\renewcommand{\labelenumii}{(\alph{enumii})} %Sets the second level of enumerate to be (a), (b), (c), .....
\renewcommand{\labelenumiii}{(\roman{enumiii})} % Sets the third level of enumerate to be (i), (ii), (iii), ....



\begin{document}
\null \vskip1cm
\begin{enumerate}

\renewcommand\labelenumi{\bfseries\theenumi.}

\item

    \begin{enumerate}
        \item Give the definition of a normal form game.
        ~\hfill{[2]}
        \item Consider the normal form game with
            the following matrix representation:
            $$A=
                \begin{pmatrix}
                    1 & -2\\
                    -2 & 1
                \end{pmatrix}
              \qquad
              B=
                \begin{pmatrix}
                    -2 & 1\\
                    1 & -2
                \end{pmatrix}
            $$

            Consider the mixed strategies for the row player
            \(\sigma_r=(x,1-x)\) and the column player \(\sigma_c=(y,1-y)\).
            Sketch a plot of:

            \begin{itemize}
                \item Of the row player's utilities: \(u_r((1, 0), \sigma_c)\)
                    and \(u_r((0, 1), \sigma_c)\).
                    ~\hfill{[1]}
                \item Of the column player's utilities: \(u_r(\sigma_r, (1, 0))\)
                    and \(u_c(\sigma_r, (0, 1))\).
                    ~\hfill{[1]}
            \end{itemize}

            Using the plot, obtain the best responses of both
            players.~\hfill{[1]}

        \item Give a proof of the following theorem:

              In a two player game $(A,B)\in{\mathbb{R}^{m\times n}}^2$ a mixed
              strategy $\sigma_r^*$  of the row player is a best response to a
              column player's strategy $\sigma_c$ if and only if:

              $${\sigma_r^*}_i > 0 \Rightarrow (A\sigma_c^T)_i =
              \max_{k}(A\sigma_c^T)_k\text{ for all }1\leq i\leq m$$

              ~\hfill{[5]}

        \item Using the above theorem, identify the Nash equilibria for the game
            in question (b) and confirm your answer to question (b).
              ~\hfill{[5]}

        \item Consider the accompanying 2017 paper entitled ``Measuring the price
            of anarchy in critical care unit interactions'' by Knight et al.

            \begin{enumerate}
                \item Give a general summary of the paper.~\hfill{[3]}
                \item What is the main theoretic result of the
                    paper?~\hfill{[2]}
                \item Identify a specific modelling assumption made that limits
                    the work.~\hfill{[2]}
                \item Propose an approach that could be used to overcome
                    this limiting factor.~\hfill{[3]}
            \end{enumerate}
    \end{enumerate}

\newpage
\item

    \begin{enumerate}
        \item Give the definition of a repeated game.
            ~\hfill{[2]}
        \item Give the definition of strategy in a repeated game.
            ~\hfill{[2]}

        \item Show that in general the total size of the history space is given
            by:

            \[
                \left|\bigcup_{t=0}^{T-1}H(t)\right| = \frac{1 - (|S_1||S_2|)^T}{1 - |S_1||S_2|}
            \]

            Where \(S_1, S_2\) are the strategy spaces for the stage game for
            both players and \(H(t)\) is the history of play at stage \(t\).
            ~\hfill{[5]}
        \item For the remainder of this question, consider the following stage
            game:

            \[
                A = \begin{pmatrix}
                    3 & 6 & 1\\
                    1 & 2 & 0\\
                    \end{pmatrix}
                \qquad
                B = \begin{pmatrix}
                    0 & 7 & 7\\
                   20 & 1 & 0\\
                    \end{pmatrix}
            \]


            Obtain all possible histories for the corresponding 2 stage repeated
            game.
            ~\hfill{[3]}


        \item Give a proof of the following theorem:

            For any repeated game, any sequence of stage Nash profiles gives a
            Nash equilibrium.
            ~\hfill{[4]}

        \item Obtain all Nash equilibria for the 2 stage repeated game of
            question (d)
            that are sequences
            of stage Nash equilibria.
            ~\hfill{[3]}

        \item Obtain a Nash equilibrium that is not a sequence of stage Nash
            equilibria for the 2 stage repeated game of question (d). Justify
            this.
            ~\hfill{[6]}


    \end{enumerate}

\newpage
\item

    \begin{enumerate}
        \item For a two player game $(A, B)\in{\mathbb{R}^{m\times n}_{>0}}^2$
            give the definition of the row/column player best response polytope.
            ~\hfill{[3]}
        \item For the remainder of this question, consider the following 
            game:

            \[
                A = \begin{pmatrix}
                    3 & 6 & 1\\
                    1 & 2 & 0\\
                    \end{pmatrix}
                \qquad
                B = \begin{pmatrix}
                    0 & 7 & 7\\
                   20 & 1 & 0\\
                    \end{pmatrix}
            \]

            Obtain the half space (inequalities) definition of the best
            response polytopes \(\mathcal{P},\mathcal{Q}\).

            ~\hfill{[5]}
         \item The vertices and corresponding labels that correspond to these
             polytopes are given by:

             For \(\mathcal{P}\):

             \begin{align*}
                 (0, 0)&\text{ with labels: }\{0, 1\}\\
                 (1/7, 0)&\text{ with labels: }\{1, 3, 4\}\\
                 (0, 1/20)&\text{ with labels: }\{0, 2\}\\
                 (19/140, 1/20)&\text{ with labels: }\{2, 3\}
             \end{align*}

             For \(\mathcal{Q}\):

             \begin{align*}
                 (0, 0, 0)&\text{ with labels: }\{2, 3, 4\}\\
                 (0, 0, 1)&\text{ with labels: }\{0, 2, 3\}\\
                 (0, 1/6, 0)&\text{ with labels: }\{0, 2, 4\}\\
                 (1/3, 0, 0)&\text{ with labels: }\{0, 3, 4\}
             \end{align*}

             Confirm that the labels listed are correct.

             ~\hfill{[4]}

         \item Describe the vertex enumeration algorithm.
             ~\hfill{[2]}

         \item Use the vertex enumeration algorithm to find all equilibria of
             the game.
             ~\hfill{[6]}

         \item Describe the Lemke-Howson algorithm for two player games.
             ~\hfill{[2]}

         \item Use the Lemke-Howson algorithm to find \textbf{a} Nash equilibria
             for the game.
             ~\hfill{[3]}
    \end{enumerate}

\newpage
\item

    \begin{enumerate}
        \item Give the definition of a Moran process on a game.
            ~\hfill{[4]}
		\item Consider a matrix $A\in\mathbb{R}^{m\times n}$ representing a
game with two strategies.

			$$ A= \begin{pmatrix} a & b\\ c & d \end{pmatrix} $$

			Let:

			$$f_{1i}=\frac{a(i-1)+b(N-i)}{N-1}$$
$$f_{2i}=\frac{c(i)+d(N-i-1)}{N-1}$$

			For the Moran process on this game, prove that the fixation
probability \(x_i\) (of \(i\) individuals of the first type taking over the
population) is given by:

			$$
x_i=\frac{1+\sum_{j=1}^{i-1}\prod_{k=1}^j\frac{f_{2k}}{f_{1k}}}{1+\sum_{j=1}^{N-1}\prod_{k=1}^j\frac{f_{2k}}{f_{1k}}}
$$

             State any results you use.

            ~\hfill{[6]}
        \item Consider the Markov process on the following game:
        \(A = \begin{pmatrix} 0 & 2\\ r & 0 \end{pmatrix}\)

            Use the above theorem to show that the fixation probability \(x_1\)
            for \(N=3\) is given by:

            \[
                \frac{1}{\frac{r^{2}}{4} + \frac{r}{4} + 1}
            \]

            ~\hfill{[6]}

            Obtain \(x_1\) for \(r=2\).

            ~\hfill{[1]}


        \item Show that a value of \(r\) that ensures \(x_1>9/10\) satisfies:
            \[
                r ^ 2 + r - 4 / 9 < 0
            \]
            ~\hfill{[4]}

            Using this, obtain a condition for \(r\) that ensures
            \(x_1>9/10\).
            ~\hfill{[3]}

            Offer an interpretation for this.
            ~\hfill{[1]}


    \end{enumerate}
\end{enumerate}


\makeatletter
\renewcommand{\@oddfoot}{\hfil \arabic{page}X \hfil}    % sets last page footer
\makeatother

\end{document}
