\documentclass[11pt,a4paper]{article}

\usepackage[margin=2cm]{geometry}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{lmodern}
\usepackage[T1]{fontenc}

\usepackage{ifxetex}
\ifxetex
  % Avoid microtype issues under XeLaTeX
\else
  \usepackage{microtype}
\fi

\usepackage{hyperref}
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfauthor={V. Knight},
  pdftitle={Stable Matching Activity: Mathematicians vs Physicists}
}

\setlength{\columnsep}{1cm}
\setlist[itemize]{noitemsep, topsep=0pt}
\titleformat{\section}{\normalfont\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalfont\normalsize\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
    {\LARGE \textbf{Mathematicians with Physicists}}\\[0.5em]
    {\large A Stable Matching Activity}\\[0.5em]
    \rule{0.9\linewidth}{0.4pt}
\end{center}

\hrulefill

\subsection*{Carl Friedrich Gauss (1777--1855)}
Gauss, often called the ``Prince of Mathematics,'' valued precision and
elegance. He preferred collaborators who respected rigor and quiet focus. He
was less interested in flashy ideas than in solid foundations.\\
\emph{Contribution:} Fundamental work in number theory, statistics, analysis,
geometry, and electromagnetism.

\subsection*{Emmy Noether (1882--1935)}
A pioneer of abstract algebra, Noether loved symmetry and generality. She
thrived with creative, inclusive collaborators and dismissed narrow or rigid
approaches.\\
\emph{Contribution:} Revealed the deep link between symmetries and conservation
laws in physics.

\subsection*{Alan Turing (1912--1954)}
Visionary and analytical, Turing admired boundary-pushing ideas in logic and
computation. He was impatient with old-fashioned approaches but enjoyed
brilliance and playful creativity.\\
\emph{Contribution:} Father of computer science; helped crack the Enigma code
in World War II.

\subsection*{Leonhard Euler (1707--1783)}
Prolific and versatile, Euler thrived on solving many problems with boundless
energy. He liked enthusiastic colleagues and disliked skeptics or show-offs.\\
\emph{Contribution:} Groundbreaking work in graph theory, analysis, and
mechanics.

\subsection*{Albert Einstein (1879--1955)}
Einstein valued bold, imaginative ideas and admired eccentric creativity. He
struggled with rigid, routine-based thinkers.\\
\emph{Contribution:} Developed the special and general theories of relativity.

\subsection*{Marie Curie (1867--1934)}
Curie respected discipline, patience, and practicality. She admired
collaborators who balanced creativity with hard work, but avoided drama.\\
\emph{Contribution:} Discovered polonium and radium; pioneered radioactivity
research.

\subsection*{Isaac Newton (1642--1727)}
Intense and ambitious, Newton respected power and clear reasoning. He liked
determined collaborators but disliked rivals.\\
\emph{Contribution:} Developed the laws of motion and gravitation;
co-invented calculus.

\subsection*{Richard Feynman (1918--1988)}
Playful and curious, Feynman thrived on excitement and fresh perspectives. He
disliked rigidity and self-importance.\\
\emph{Contribution:} Advanced quantum electrodynamics; known as a brilliant
physics communicator.


\end{document}
